???A quantitative framework for investigating the reliability of network construction

### 2017-09-17 manuscript/CI_interactions.tex
added a better code snippet for making the prior web and calculating degree distributions

      prior_web=read.csv(path_to_Dryad_file)
      deg_dist_Salix=with(prior_web,tapply(gall_total_rich,Genotype,mean))/4
      gallers=cbind(prior_web$Genotype,prior_web[,27:30])
      aSG_means=with(prior_web,tapply(aSG_abund,Genotype,mean))
      rG_means=with(prior_web,tapply(rG_abund,Genotype,mean))
      vLG_means=with(prior_web,tapply(vLG_abund,Genotype,mean))
      SG_means=with(prior_web,tapply(SG_abund,Genotype,mean))
      deg_dist_galler=c(length(which(aSG_means>0)),length(which(rG_means>0)),length(which(SG_means>0)),length(which(rG_means>0))      )/26
      int_probs=as.numeric(deg_dist_galler\%*\%t(deg_dist_Salix))

      pars=fitdistr(x=int_probs,"beta",start=list(shape1=1,shape2=1))$estimate
      alpha=pars[[1]]
      beta=pars[[2]]
      mu=alpha/(alpha+beta)
      num=alpha*beta
      den=(alpha+beta)**2*(alpha+beta)
      sigma2=num/den

      [[Checking this for reasonableness: sum is about 30, so we should have 30 galler-genotype combinations?]]

      Using this degree distribution we can obtain prior values for $\alpha$ and $\beta$ using the code above. We obtain
      $\alpha$=2.175656, $\beta$=5.361083.

      For species where no co-occurances were observed, we can calculate the MLE estimates for the mean and variance of $\omega_{ij}$ directly from this prior. These are:
      $\hat{\omega_{ij}}$=0.2886734, var($\omega$)=0.02724535.

@@

      $\hat{\omega_{ij}}$=0.005702349, var($\omega$)=1.486051e-05.

      Realistic values for n when k=0, based on a sample of 20 random sites:
      n=1: 0.25485794 0.02224566
      n=2: 0.22813413 0.01846427
      n=3: 0.20648283 0.01555013
      n=4: 0.18858498 0.01326377

>>>>

      prior_web_data=read.csv(path_to_Dryad_file)
      # Remove extra data on parasitoids, etc.
      prior_web_data[,31:57]<-NULL
      prior_web_data[,4:26]<-NULL
      prior_web_data[,2]<-NULL
      # Build a web with interactions=1 for any galler observed on any genotype
      prior_web=matrix(nrow=26,ncol=4)
      for(r in 1:length(levels(prior_web_data$Genotype))){
        gen=levels(prior_web_data$Genotype)[r]
        subset=prior_web_data[which(prior_web_data$Genotype==gen),]
        for(c in 1:4){
          if(sum(subset[,2+c])>0){
            prior_web[r,c]=1
          } else {
            prior_web[r,c]=0
          }
        }        
      }
      # Now get the degree distributions from the web
      deg_dist_Salix=rowSums(prior_web)/ncol(prior_web)
      # Remove one genotype that never interacted
      deg_dist_Salix<-deg_dist_Salix[which(rowSums(prior_web)>0)]
      deg_dist_galler=colSums(prior_web)/nrow(prior_web)
      # Interaction probabilities are the product of plant and galler probabilities
      int_probs=as.numeric(deg_dist_galler%*%t(deg_dist_Salix))

      Using this degree distribution we can obtain prior values for $\alpha$ and $\beta$ using the code above. We obtain
      $\alpha$=2.807855, $\beta$=2.342815.

      For species where no co-occurances were observed, we can calculate the MLE estimates for the mean and variance of $\omega_{ij}$ directly from this prior. These are:
      $\hat{\omega_{ij}}$=0.5451437, var($\omega$)=0.0481417.
      This is consistent with the prior data, where the average interaction probability based on the degree distributions of Salix genotypes and gallers was 0.541. It may not be consistent with the degree distributions in our current dataset, however, especially since we are concerned with Salix species rather than genotypes within a species. We therefore want to update our distribution using known data from known co-occurances between species.

@@

      $\hat{\omega_{ij}}$=7.405645e-03, var($\omega$)=1.938755e-05.

      Realistic values for n when k=0, based on a sample of 20 random sites:
      n=1: 0.4565121 0.0403385
      n=2: 0.39267022 0.03335076
      n=3: 0.34449379 0.02770543
      n=4: 0.30684696 0.02324331
